|

### 2020-03-09 paper/paper_3_sim.Rmd
marching along

## Visualizing a run
```{r}
# ADD IN CODE THAT GENERATES THIS
out <- read_rds(here("paper/paper_3_out2.rds"))
```
Figure \ref{fig:difmap} provides intuition about the data generating process by showing the relationship between $\theta_i$ and $Pr(y_{ij} = 1)$ with $\eta_i$ set to the group mean. The items are ordered by the amount of DIF such that $\angle_{j = 11} = 30^\circ$ up to $\angle_{j = 20} = 60^\circ$.
```{r difmap, fig.cap = 'For a 20 item test, the relationship between target ability and probability of correct response with nuisance abilities fixed to group means.', out.width="70%", warning = FALSE, message = FALSE}
out$bigsim[[2]]$pars[[4]] %>% 
  graph_pars_noncompensatory(0, -1) +
  scale_y_continuous(labels = scales::percent) +
  labs(
    x = latex2exp::TeX("$\\theta_i$"),
    y = latex2exp::TeX("$Pr(y_{ij} = 1)$")
  )
```

>>>>

## Visualizing a run
```{r}
# ADD IN CODE THAT GENERATES THIS
out <- read_rds(here("paper/paper_3_out1.rds"))

out <-
    out %>%
    mutate(bigsim = map2(bigsim, n_dif_items, add_foc_mean))

# i have no idea why this is like this...
out %>% 
  mutate(bigsim = bigsim %>% map(~ select(., foc_mean))) %>% 
  unnest(bigsim) %>% 
  ggplot(aes(x = n_dif_items, y = foc_mean)) +
  geom_point()

out$bigsim[[4]]$p[[1]] %>% colMeans()

```
Figure \ref{fig:difmap} provides intuition about the data generating process by showing the relationship between $\theta_i$ and $Pr(y_{ij} = 1)$ with $\eta_i$ set to the group mean. The items are ordered by the amount of DIF such that $\angle_{j = 11} = 30^\circ$ up to $\angle_{j = 20} = 60^\circ$.
```{r difmap, fig.cap = 'For a 20 item test, the relationship between target ability and probability of correct response with nuisance abilities fixed to group means.', out.width="70%", warning = FALSE, message = FALSE}
out$bigsim[[2]]$pars[[4]] %>% 
  graph_pars_noncompensatory(0, -1) +
  scale_y_continuous(labels = scales::percent) +
  labs(
    x = latex2exp::TeX("$\\theta_i$"),
    y = latex2exp::TeX("$Pr(y_{ij} = 1)$")
  )
```
